\documentclass[10pt, a4paper]{article}

\usepackage[margin=2cm]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}

\pagestyle{empty}
\setlength{\parindent}{0pt}

% ── Colors ──────────────────────────────────────────────
\definecolor{accent}{HTML}{2C3E50}
\definecolor{linkcolor}{HTML}{2980B9}
\definecolor{graytext}{HTML}{555555}

% ── Hyperlinks ──────────────────────────────────────────
\hypersetup{
    colorlinks=true,
    urlcolor=linkcolor,
    linkcolor=accent,
}

% ── Item styling ───────────────────────────────────────
\setlist[itemize]{
    leftmargin=1.4em,
    itemsep=1pt,
    parsep=0pt,
    topsep=2pt,
    labelsep=4pt,
}
\setlength{\itemindent}{0pt}

% ── Section command ────────────────────────────────────
\newcommand{\heading}[1]{%
    \vspace{8pt}%
    {\color{accent}\large\bfseries #1}\\[-2pt]%
    \textcolor{accent}{\rule{\textwidth}{0.4pt}}%
    \vspace{4pt}%
}

% ── Role entry command ─────────────────────────────────
\newcommand{\roleentry}[3]{%
    \vspace{2pt}%
    {#1 \hfill {\small\color{graytext}#3}}\\[1pt]%
    {\textbf{#2}}%
    \vspace{1pt}%
}

\begin{document}

% ── Header ──────────────────────────────────────────────
\begin{center}
    {\color{accent}\LARGE\bfseries Yury Bely}\\[8pt]
    {\small
    \href{mailto:yury.bely@icloud.com}{yury.bely@icloud.com}
    \enspace\color{graytext}$\bullet$\color{black}\enspace
    \href{https://linkedin.com/in/yurybely}{linkedin.com/in/yurybely}
    \enspace\color{graytext}$\bullet$\color{black}\enspace
    \href{https://github.com/teremo4ek}{github.com/teremo4ek}}
\end{center}

\vspace{8pt}

\noindent\color{graytext}\small
Software Engineer with 15+ years of experience in systems and cross-platform development (C++, Rust).\\
Built desktop, mobile, and real-time applications across Windows, Linux, macOS, Android, and iOS.\\
Strong background in performance optimization, networking, and low-level system architecture.\\
Experience with AI-assisted development and LLM integration.

% ── Experience ──────────────────────────────────────────
\heading{Professional Experience}

\roleentry{ScienceSoft | Global IT software development}{Rust Developer}{2024 -- 2025}
\begin{itemize}
    \item Built cross-platform desktop applications using Rust, Tauri, and Vue.js for Windows, macOS, and Linux.
    \item Reduced application memory footprint by \textasciitilde 10\% compared to Electron-based alternatives.
    \item Improved startup time by \textasciitilde 2x through native integration and optimized resource loading.
\end{itemize}

\roleentry{ScienceSoft | Global IT software development}{Senior C++ Developer}{2021 -- 2024}
\begin{itemize}
    \item Contributed to development of Oracle-compatible functionality for an enterprise RDBMS, implementing support for PL/SQL-like syntax and behavior.
    \item Built an Oracle compatibility mode enabling seamless migration by switching connection strings without changes to business logic or SQL queries.
    \item Implemented and validated support for hundreds of SQL/PLSQL constructs, including procedures, functions, and triggers.
    \item Resolved compatibility edge cases between Oracle and target DB, ensuring consistent query execution behavior.
    \item Reduced migration effort from months to days for existing enterprise systems.
    \item Ensured full backward compatibility with native database mode.
\end{itemize}

\roleentry{ScienceSoft | Global IT software development}{Senior C++ Developer}{2017 -- 2021}
\begin{itemize}
    \item Collaborated in a 30+ engineer cross-functional team to build a secure cross-platform video conferencing application.
    \item Built and maintained a shared C++ core library used across 4 platforms (iOS, Android, Windows, macOS), reducing code duplication and ensuring consistent behavior.
    \item Introduced adaptive media management supporting real-time speaker detection in calls with 5+ participants.
    \item Implemented local storage handling thousands of messages and session records per user, improving data reliability.
    \item Strengthened end-to-end encryption by replacing WebRTC SSL with OpenSSL, improving security compliance and control over cryptographic stack.
    \item Resolved concurrency issues and reduced crash rate on mobile platforms by \textasciitilde 25\%.
    \item Created internal testing and support tools, improving SDK reliability.
\end{itemize}

\roleentry{ScienceSoft | Global IT software development}{Senior C++ Developer}{2016 -- 2017}
\begin{itemize}
    \item Built a medical software system for auditory hallucination treatment with real-time VoIP and voice transformation.
    \item Designed system architecture and developed a QML-based UI.
    \item Prototyped a system to improve GPS positioning accuracy using Real-Time Kinematic (RTK) and Continuously Operating Reference Stations (CORS) techniques.
\end{itemize}

\roleentry{ScienceSoft | Global IT software development}{Xamarin Developer, .NET Developer}{2015 -- 2016}
\begin{itemize}
    \item Built mobile applications integrating GPS, camera, and push notifications.
    \item Published applications to App Store and Google Play.
    \item Created an interactive 3D exhibition preview application in Unity.
\end{itemize}

\roleentry{ScienceSoft | Global IT software development}{Senior C++ Developer}{2014 -- 2015}
\begin{itemize}
    \item Built a desktop music streaming application based on WebKit with deep OS-level integration.
    \item Architected and built a real-time desktop and webcam streaming application.
    \item Implemented video capture and frame processing using OpenCV.
    \item Added audio streaming and mixing via GStreamer/FMOD.
    \item Integrated RTSP client for real-time video transmission.
    \item Delivered a Windows-based solution using C++, Qt, and STL.
\end{itemize}

\roleentry{ScienceSoft | Global IT software development}{Senior C++ Developer}{2012 -- 2014}
\begin{itemize}
    \item Ported a feature-rich Chromium-based browser to Windows, adding native support for torrent handling without the need for third-party applications.
    \item Contributed to interface localization and platform-specific adaptations.
    \item Built a video search and download manager with support for multiple formats and integration with leading video platforms (YouTube, Vimeo, Dailymotion, etc.), featuring an embedded video player.
    \item Built a feature-rich download manager with BitTorrent support and plugin architecture.
\end{itemize}

\roleentry{ScienceSoft | Global IT software development}{C++ Developer}{2011 -- 2012}
\begin{itemize}
    \item Integrated and maintained social network functionality via the Facebook API.
    \item Developed JavaScript solutions for interacting with Facebook services, improving automation and efficiency.
\end{itemize}

\roleentry{Science Research Institute of Means of Automation}{Junior C++ Developer}{2007 -- 2011}
\begin{itemize}
    \item Built a cross-platform application using Qt, implementing a complex UI and highly customized, non-standard design solutions.
\end{itemize}

% ── Education ───────────────────────────────────────────
\heading{Education}

\roleentry{Belarusian State University of Informatics and Radioelectronics}{Bachelor of Computer Science}{2002 -- 2007}

% ── Languages ───────────────────────────────────────────
\heading{Languages}

English (B2), German (A1)

% ── Skills ──────────────────────────────────────────────
\heading{Skills}

\noindent
\textbf{Languages:} C++, Rust, Python, C\#, Swift, SQL, JS/TS\\[2pt]
\textbf{Frameworks:} Qt, QML, Tauri, Djinni, OpenCV, WebRTC\\[2pt]
\textbf{Databases:} SQLite, PostgreSQL, Oracle\\[2pt]
\textbf{Platforms:} Windows, Linux, macOS, Android, iOS\\[2pt]
\textbf{Tools:} Git, Docker, CMake, CI/CD, VS, Xcode\\[2pt]
\textbf{AI \& LLM:} Claude Code, Copilot, ChatGPT, Ollama, prompt engineering

\end{document}
